### 2022-08-19 README.qmd
anonymised further (removed anything pointing to original git repo and user

# AlgorithmicRecourseDynamics.jl - Research Paper 📝

**Note** ⚠: You are on the `#original-paper` branch of `AlgorithmicRecourseDynamics.jl`. This branch is a static artifact corresponding to the state of the package at the time the paper was first published. It can be used to replicate the original findings of the paper. For an up-to-date version of the package, please switch to the [`#main`](https://github.com/pat-alt/AlgorithmicRecourseDynamics.jl) branch.

@@

- [Paper](paper/paper.pdf)
- [Notebooks](dev/notebooks/)
- [Artifacts](https://github.com/pat-alt/AlgorithmicRecourseDynamics.jl/releases/tag/artifacts) (including data and experimental results)

>>>>

# AlgorithmicRecourseDynamics

`AlgorithmicRecourseDynamics.jl` is a Julia package for modelling Algorithmic Recourse Dynamics.

## Research Paper 📝

**Note** ⚠: You are browsing the `#original-paper` branch of `AlgorithmicRecourseDynamics.jl`. This branch is a static artifact corresponding to the state of the package at the time the paper was first published. It can be used to replicate the original findings of the paper. Only this branch is currently accessible as an anonymised git repository. The main repository is private and will will be open-sourced after the review process.

@@

- [Paper](paper/paper.pdf)
- [Notebooks](dev/notebooks/)
- [Supplementary Appendix](build/dev/notebooks/appendix.html) (download the HTML and view in browser)
- [Artifacts]() (including data and experimental results; link currently exluded due to double-blind review)
